Extracting data for time slice analyses

### 2017-11-23 analyses/01-extract-data-for-analyses.Rmd
Remove unneeded comment
Add Bapst et al data

```{r, eval = TRUE}
# The latest version of devtools and ape
library(devtools)
library(ape)

@@

## The latest version of dispRity 
install_github("TGuillerme/dispRity", ref = "master")
library(dispRity) 
```

@@

Running these extractions for other datasets
===================================================

@@

```{r}
## Setting up the slug names
slug <- "Wright2017"

@@

# Loop
```{r}
## Setting up the slug names
slugs <- c("Bapst2016", "Hopkins", "Other")

# Big old loop (too lazy to make functions sorry!)
for(slug in 1: length(slugs)) {

## Loading the data
matrix <- ReadMorphNexus(paste0("../data/matrices/", slugs[slug], ".nex"))
FADLAD <- read.csv(paste0("../data/FADLAD/", slugs[slug], ".csv"), row.names = 1, header = TRUE)
tree <- read.nexus(paste0("../data/trees/", slugs[slug], ".tre"))

[MCC tree. Note that to properly timescale the tree [e.g., in R] you must first divide the branch lengths by the corresponding clock rate, (= 0.03517385), and then set the root.time to 485.4]

@@

## Estimating the ancestral states (with a uncertainty threshold of 0.95)
matrix_nodes <- AncStateEstMatrix(matrix, tree, estimate.allchars = TRUE,
                                  uncertainty.threshold = 0.95)
save(matrix_nodes, file = paste0("../data/processed/ancestral_states.", slugs[slug] ,".Rda"))

## Add ancestral states to nodes
load(paste0("../data/processed/ancestral_states.", slugs[slug] ,".Rda"))
row.names(matrix_nodes) <- tree$node.label
matrix$matrix <- rbind(matrix$matrix, matrix_nodes)

## Constructing the distance matrix
matrix_dist <- MorphDistMatrixFast(matrix, distance = "Gower")
save(matrix_dist, file = paste0("../data/processed/distance_matrix.", slugs[slug] ,".Rda"))

## Ordinating the matrix - no need to run this here, we will do this in the next script
## load(paste0("../data/processed/distance_matrix.", slugs[slug] ,".Rda"))
## morphospace <- cmdscale(matrix_dist, k = nrow(matrix_dist) - 2, add = TRUE)$points

}
```

>>>>

```{r, eval = TRUE, message = FALSE}
# The latest version of devtools and ape
library(devtools)
library(ape)

@@

## The latest version of dispRity 
install_github("TGuillerme/dispRity", ref = "release")
library(dispRity) 
```

@@

Running these extractions for other datasets
===================================================
Ideally we'd have written functions to do this, and/or a big old loop. But each dataset was slightly different so we've dealt with each individually.

@@

```{r}
slug <- "Wright2017"

@@

Bapst et al 2016 Biol Letters
-----------

```{r}
slug <- "Bapst2016"

## Loading the data
matrix <- ReadMorphNexus(paste0("../data/matrices/", slug, ".nex"))
FADLAD <- read.csv(paste0("../data/FADLAD/", slug, ".csv"), row.names = 1, header = TRUE)
# Note that these are the upper bound for FAD and lower bound for LAD
tree <- read.nexus(paste0("../data/trees/", slug, ".nex"))

@@

## Constructing the distance matrix
matrix_dist <- MorphDistMatrixFast(matrix, distance = "Gower")
save(matrix_dist, file = paste0("../data/processed/distance_matrix.", slug ,".Rda"))

## Ordinating the matrix - no need to run this here, we will do this in the next script
## load(paste0("../data/processed/distance_matrix.", slugs[slug] ,".Rda"))
## morphospace <- cmdscale(matrix_dist, k = nrow(matrix_dist) - 2, add = TRUE)$points
```

Bapst et al 2016 Biol Letters
-----------

```{r}
slug <- "Bapst2016"

## Constructing the distance matrix
matrix_dist <- MorphDistMatrixFast(matrix, distance = "Gower")
save(matrix_dist, file = paste0("../data/processed/distance_matrix.", slug ,".Rda"))

## Ordinating the matrix - no need to run this here, we will do this in the next script
## load(paste0("../data/processed/distance_matrix.", slugs[slug] ,".Rda"))
## morphospace <- cmdscale(matrix_dist, k = nrow(matrix_dist) - 2, add = TRUE)$points
```

Bapst et al 2016 Biol Letters
-----------

```{r}
slug <- "Bapst2016"

## Constructing the distance matrix
matrix_dist <- MorphDistMatrixFast(matrix, distance = "Gower")
save(matrix_dist, file = paste0("../data/processed/distance_matrix.", slug ,".Rda"))

## Ordinating the matrix - no need to run this here, we will do this in the next script
## load(paste0("../data/processed/distance_matrix.", slugs[slug] ,".Rda"))
## morphospace <- cmdscale(matrix_dist, k = nrow(matrix_dist) - 2, add = TRUE)$points
```

Bapst et al 2016 Biol Letters
-----------

```{r}
slug <- "Bapst2016"

## Constructing the distance matrix
matrix_dist <- MorphDistMatrixFast(matrix, distance = "Gower")
save(matrix_dist, file = paste0("../data/processed/distance_matrix.", slug ,".Rda"))

## Ordinating the matrix - no need to run this here, we will do this in the next script
## load(paste0("../data/processed/distance_matrix.", slugs[slug] ,".Rda"))
## morphospace <- cmdscale(matrix_dist, k = nrow(matrix_dist) - 2, add = TRUE)$points
```
Bapst et al 2016 Biol Letters
-----------

```{r}
slug <- "Bapst2016"

## Constructing the distance matrix
matrix_dist <- MorphDistMatrixFast(matrix, distance = "Gower")
save(matrix_dist, file = paste0("../data/processed/distance_matrix.", slug ,".Rda"))

## Ordinating the matrix - no need to run this here, we will do this in the next script
## load(paste0("../data/processed/distance_matrix.", slugs[slug] ,".Rda"))
## morphospace <- cmdscale(matrix_dist, k = nrow(matrix_dist) - 2, add = TRUE)$points
```
